---
title: "R Notebook"
output: html_notebook
author: Georgia Doing georgia.doing.gr@dartmouth.edu
date crated: 
date modified: Sys.Date()
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Intro:

Overdispersion: varaince > mean
Code

```{python}
def zinbl2(y_true,y_pred):
	y_true = tf.cast(y_true, tf.float32)
	y_pred = tf.cast(y_pred, tf.float32)
	eps = 1e-10 
	theta = 1e6
	pi = 0.5
	ridge_lambda = 0
	t1 = tf.math.lgamma(1e6 + 1e-10) + tf.math.lgamma(y_true + 1.0) - tf.math.lgamma(y_true+1e6+1e-10)
	t2 = (1e6+y_true) * tf.math.log(1.0 + (y_pred/(1e6+1e-10))) + (y_true * (tf.math.log(1e6+1e-10) - tf.math.log(y_pred + 1e-10)))

	nb_case = t1+t2 - tf.math.log(1.0 - pi+eps)

	zero_nb = tf.pow(theta/(theta+y_pred+eps), theta)
	zero_case = -tf.math.log(pi + (( 1.0-pi)*zero_nb)+eps)
	result = tf.where(tf.less(y_true,1e-8), zero_case, nb_case)
	ridge = ridge_lambda*tf.square(pi)
	result += ridge


	final = tf.reduce_mean(result)
	return _nan2inf(final)
```


Pseudocode:

Cast predicted and true data into float32
Set vars
  eps as 1e-10 (for numerical stability, set as constant)
  theta as 1e6 (dispersion)
  pi as 0.5 (zero inflation)
  lambda as 0 (ridge - Lnorm?)
    
Calc tensor 1 as
  log(abs(gamma(eps+theta))) + log(abs(gamma(true data+1))) - log(abs(gamma(true data+eps+theta)))
  
Calc tensor 2 as 
  (1e6+true data) * log(1+ (predicted data/(1e6+1e-10))) + true data * log(1e6+1e-10 - log(predicted data + 1e-10))

Calc NB case as
  tensor 1 + tensor 2 - log(1 - pi + eps)
  
Calc ZINB as
  (theta / (predicted data + theta + eps)) ** theta
  
Calc zero case as
  - log(pi + ((1-pi) * ZINB) + eps)
  
Calc result as
  If true data < 1e-8, zero case
  else, NB case
  
Calc ridge as
  lambda * pi**2
  
Sum result and ridge for all predicted features, return mean

Equation:

$$ log(|\Gamma(\epsilon+\theta)|) + log(|\Gamma{Y+1}|) - log(|\Gamma{Y+\epsilon+\theta}|) \\ + \\ (\theta + Y) \cdot log(1+\frac{Y'}{\theta+\epsilon}) + Y \cdot log(\theta+\epsilon)-log(Y'+\epsilon))$$
```{r}
png('nb_dists.png')
x1 <- rnbinom(500, mu = 4, size = 1)
x2 <- rnbinom(500, mu = 4, size = 3)
x3 <- rnbinom(500, mu = 4, size = 1e6) # size = dispersion here
h1 <- hist(x1, breaks = 20, plot = FALSE)
h2 <- hist(x2, breaks = h1$breaks, plot = FALSE)
h3 <- hist(x3, breaks = h1$breaks, plot = FALSE)
barplot(rbind(h1$counts, h2$counts, h3$counts),
        beside = TRUE, col = c("red","blue","cyan"),
        names.arg = round(h1$breaks[-length(h1$breaks)]))
dev.off()
```

# Log Liklihood

$$log_e(L) = log_{e}(L(p|n,y)) = log_{e} \binom{n}{y}  + y \cdot log_e(p) + (n-y) \cdot log_e(1-p) $$
## Background

## Purpose

## Outline

## Reflections